Estimating real-time highstreet footfall from Wi-Fi probe requests

### 2018-06-26 paper/sections/main_study.tex
main study progress

The aims of the main study are,
test the validity of the signal strength algorithm in different 
micro site conditions.
Test that the sequence number algorithm works in real world
for different locations and different times.
check if the thresholds are consistent.
Test if the calibration works over intervals
Finally conclude if we can estimate footfall confidently
with just probe requests.

five locations were selected across central london which
had different types of configurations and specific problems
configuratons are shown in fig. map is shown in figure.
\begin{enumerate}
	\item Phone Shop Camden - has phones and bus stops.
	\item Restaurant TCR - has seating area on either side.
	\item Holborn Information Kiosk - High volumne station entry
	\item Restaurant Russell Square - seating on one side and side walk on other
	\item Shop Charring Cross - sidewalk on one side and phone shop next door
\end{enumerate}
Installations were carried out over the time period from xxxx to xxxx.
the data collection happened from xxxx to xxxx. Manual counting was carried out
with high precision on dates xxxx and aggregated five minutes on xxxx.
The difference in methods could lead to some inaccuracies in data.
The overall schedule is shown in half page graphic.

The overall statistics of data collected. How many probe requests.
Comparision of location in terms of volume, patterns in daily footfall etc.
The comparision between global and local.
comparision between different types of vendors.
Specifics on top 5 manufacturers.

>>>>

The main study was designed to validate the results of the pilot study over different locations at different times. 
We choose five different locations across central London, to install the sensors and collect data for a long period of time. 
We also carry out manual counting on these locations along with this across different time of the day. 
We then apply the filtering based on signal strength and sequence numbers and compare with manual counts and evaluate the effectiveness of the process with the mean error per minute on these locations. 
Finally we calculate the ajustment factor for the first interval of manual counts and check if that works on the consecutive intervals.

The locations where the data were collected are shown in the table. The location are chosen for their variety of configuration and sources of noise. Location 1 is the `cleanest' of while location 2 is the one with the most complexity. The configuration, installation and data collection schedule is shown in the figure.

\begin{figure}
	\begin{center}
		\includegraphics [width=\linewidth] {images/main_schedule.jpeg}
		\caption{Clustering probe requests based on increasing sequence numbers present in them. The dots are individual probe requests and the red lines connect probe requests within the same cluster which are generated by the same mobile device.}
		\label{pilot_clustering}
	\end{center}
\end{figure}

\begin{table}
	\tbl{Locations where sensors were installed}
	{\begin{tabular}{clll} 
		\toprule
		 ID & Location & Type & Installation notes\\
		 \midrule
		 1 & Camden High Street & Phone Shop & Bus stop in front\\
		 2 & Central St.Giles Piazza & Restaurant & Seating area on both sides\\
		 3 & Holborn Underground Station & Information Kiosk & Overlooks station entrance\\
		 4 & Brunswick Center & Fast Food Restaurant & Has seating area on one side\\
		 5 & The Strand & Regular Shop & Has phone shop next door \\
		 \bottomrule
	\end{tabular}}
	% \tabnote{\textsuperscript{a}This footnote shows how to include footnotes to a table if required.}
	\label{locations-table}
\end{table}

\begin{figure}
	\centering
	\subfigure[Distribution of signal strengths showing the filtering of background noise]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 6 20 6,clip]{images/main_configs.jpeg}}}\hspace{20pt}
	\subfigure[Clustering probe requests as nodes in a graph using increasing sequence numbers]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 6 25 6,clip]{images/main_signals.jpeg}}}
	\caption{Schematic diagrams explaining the methods for filtering by signal strength and clustering using sequence numbers} \label{methodology_schematic}
\end{figure}

The comparision between global and local.
comparision between different types of vendors.
Specifics on top 5 manufacturers.

### 2018-06-26 paper/sections/pilot_study.tex
main study progress

\begin{figure}
	\begin{center}
		\includegraphics [width=0.95\linewidth] {images/pilot_clustering.jpeg}
		\caption{Clustering probe requests based on increasing sequence numbers present in them. The dots are individual probe requests and the red lines connect probe requests within the same cluster which are generated by the same mobile device.}
		\label{pilot_clustering}
	\end{center}
\end{figure}

@@

We then move on to assign an unique field identifying the mobile device generating the probe requests.
For the 45\% of the probe requests which were not randomised, we kept the MAC addresses as the unique identifier.
For the rest of the probe requests we applied the clustering algorithm to assign the unique identifier.
With the help of the known stationary device (the mobile device used by the surveyor to record pedestrians manually) and through trail and error, We found the suitable time threshold, $\alpha$ to be 15 seconds and threshold for sequence numbers, $\beta$ to be 60.
Figure \ref{pilot_clustering} shows the clustering of probe requests.
We finally combine both normal and anonymised probe requests, aggregate them based on their unique identifier which further reduced the mean error to -18\%.

\begin{figure}
	\begin{center}
		\includegraphics [width=0.90\linewidth] {images/pilot_comparison.jpeg}
		\caption{Comparision of counts after filtering with manual counts}
		\label{pilot_comparison}
	\end{center}
\end{figure}

>>>>

\begin{figure}
	\centering
	\subfigure[Clustering probe requests based on increasing sequence numbers present in them.]{
		\resizebox*{0.45\linewidth}{!}{\includegraphics{images/pilot_clustering.jpeg}}}\hspace{20pt}
	\subfigure[Comparision of counts after filtering with manual counts]{
	\resizebox*{0.45\linewidth}{!}{\includegraphics{images/pilot_comparison.jpeg}}}
	\caption{The results of the clustering process and the comparison with ground truth} \label{methodology_schematic}
\end{figure}

@@

We then move on to assign an unique field identifying the mobile device generating the probe requests.
For the 45\% of the probe requests which were not randomised, we kept the MAC addresses as the unique identifier.
For the rest of the probe requests we applied the clustering algorithm to assign the unique identifier.
With the help of the known stationary device (the mobile device used by the surveyor to record pedestrians manually) and through trail and error, We found the suitable time threshold, $\alpha$ to be 15 seconds and threshold for sequence numbers, $\beta$ to be 60.
Figure \ref{pilot_clustering} shows the clustering of probe requests.
The dots are individual probe requests and the red lines connect probe requests within the same cluster which are generated by the same mobile device.
We finally combine both normal and anonymised probe requests, aggregate them based on their unique identifier which further reduced the mean error to -18\%.
